\documentclass[12pt]{article}

\usepackage{latexsym}
\usepackage{amsfonts}
\usepackage{amsmath, amsthm, amssymb}


\setlength{\textheight}{10in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{-1.0in}
\setlength{\parskip}{0.15in}
\setlength{\oddsidemargin}{-0.1in}

\newcommand{\DS} [1] {${\displaystyle #1}$}

\begin{document}
\thispagestyle{empty}

\begin{center}
        \textbf{Math 2311  - Assignment 1}\\
        Due: Wed., Jan. 26th
\end{center}

{\bf Note:} You may work alone or in pairs on the assignment. If you work in a pair, hand in one assignment with both names on it. If you work in a pair, you should still be able to explain your answer to every question on the assignment.


\begin{enumerate}


        \item
              Determine if each of the following sets is a vector space.  If it is, write a convincing argument to show that it is (verify all of the axioms, or briefly explain why you only need to verify a small number of them); if it is not a vector space demonstrate at least one of the axioms that fails.
              \begin{enumerate}
                      \item \DS{ \left\{ \left[ \begin{array}{c}
                                                    x \\
                                                    y
                                            \end{array} \right] \in \mathbb{R}^2 \ | \ x \geq y \right\}} with the usual scalar multiplication and vector addition from $\mathbb{R}^2$
                      \item \DS{ \left\{f\in F (-\infty, \infty)\ | {f (1) = 0} \right\}} with the usual scalar multiplication and vector addition from $F(-\infty, \infty)$
              \end{enumerate}

        \item
              Let $V$ be a vector space.
              \begin{enumerate}
                      \item If $k$ is any scalar, prove that $k\vec{0} = \vec{0}$.
                      \item Prove that the zero vector in $V$ is unique. (Hint: assume that there are two different ``zero vectors'' and show that they must be equal to each other.)
              \end{enumerate}


        \item
              Determine if each of the following are subspaces of $M_{nn}$
              \begin{enumerate}
                      \item \DS{ \left\{A \in M_{nn} \ | det(A) = 0 \right\}}
                      \item \DS{ \left\{A \in M_{nn} \ | tr(A) = 0 \right\}} Note: $tr(A)$ is the \emph{trace} of $A$ and is equal to the sum of the diagonal entries of $A$, see section 1.3 of the text. In particular, you may use the results of questions 35 and TF question (j) from section 1.3 (11th or 12th edition).
                      \item \DS{ \left\{A \in M_{nn} \ | A^T = A \right\}} In other words, the symmetric matrices. Theorem 1.4.8 from section 1.4 may be of use.
              \end{enumerate}

        \item Consider the following vectors in $P_2$: $p_1 = 2 + x + 4x^2$, $p_2 = 1 - x + 3x^2$, $p_3 = 3 + 2x + 5x^2$.
              \begin{enumerate}
                      \item Express the vector $g = 6 + 11x + 6x^2$ as a linear combination of $p_1,p_2,p_3$.
                      \item Does $\{p_1,p_2,p_3\}$ span $P_2$?
                      \item Is $\{p_1,p_2,p_3\}$ linearly independent?
              \end{enumerate}


              %\item
              %Consider the following matrix
              %$$
              %A = \left[ \begin{array}{cccc}
              %1 & 1 & 1 & 1 \\
              %1 & 2 & 1 & 4 \\
              %2 & 3 & 2 & 6 \\
              %2 & 4 & 2 & 9
              %\end{array} \right]
              %$$
              %\begin{enumerate}
              %\item Find all solutions to the equation $A\vec{x} = \vec{0}$.
              %\item Show that the set of all solutions from (a) is a subspace of $\mathbb{R}^4$.
              %\item Let $A$ be any $m \times n$ matrix.  Show that the set of solutions to the equation $A\vec{x} = \vec{0}$ is a subspace of $\mathbb{R}^n$.
              %\end{enumerate}

        \item Consider the following planes in $\mathbb{R}^3$. $P_1: 2x + 3y - z = 0$ and $P_2: x + 2y - 2z = 0$
              \begin{enumerate}
                      \item Find a set of vectors that spans $P_1$.
                      \item Find a set of vectors that spans $P_2$.
                      \item Find a set of vectors that spans the intersection of $P_1$ and $P_2$. (Recall that we showed the intersection of two subspaces is a subspace).
              \end{enumerate}

              \item Show that the functions $f_1(x) = e^x$, $f_2(x) = xe^x$, and $f_3(x) = x^2e^x$ are linearly independent in $C^{\infty}(-\infty, \infty)$.


\end{enumerate}
\end{document}
